---
title: "Scraping from BasketballRef"
author: "Jarred Robidoux"
date: "2/10/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# __Scraping from BasketballRef__
In order to scrape from BasketballReference.com, we are going to need to utilize
the "rvest" and "dplyr" packages within R. 

# __Load Packages__
Let's load the required packages.
```{r}
#install.packages("rvest")
library(rvest)
#install.packages("dplyr")
library(dplyr)
#install.packages("janitor")
library(janitor)
#install.packages("stringr")
library(stringr)
#install.packages("ggplot2")
library(ggplot2)
#install.packages("prismatic")
library(prismatic)
#install.packages("ggrepel")
library(ggrepel)
```

# __Pull the Data__
```{r}
# Upload the link of the site where the data will be coming from 
link <-  "https://www.basketball-reference.com/leagues/NBA_2023.html"
# Create "page" object and that sends "link" through the read_html() function
full_table <- read_html(link, as.data.frame=T, stringsAsFactors=T)

# html_nodes to pull all nodes under the "table" label 
adv <- full_table %>%
  html_nodes("table")%>%
  .[[11]] %>%
  html_table(fill=T)
```

# __Manipulate Data__
Let's tidy up our adv dataframe so it is easier to plot
```{r}
# make 1 row column names 
adv <- adv %>% row_to_names(1)
colnames(adv) <- make.unique(names(adv))

# remove league average row 
adv <- adv[(!adv$Team == "League Average"),]

# remove all NAs
adv <- adv[,colSums(is.na(adv))<nrow(adv)]

# remove *s
adv$Team <- (str_remove(adv$Team, "[*]"))
```

# __Plot the Data__
Now it's time to plot our data. We are going to create a scatterplot that compares
the Offensive Rating and Defensive Rating of Teams this NBA Season. 
```{r}
# Create custom theme for the plot 
theme_jelly <- function(){
  theme_minimal(base_size = 12, base_family = "Comic Sans MS") %+replace%
    theme(
      panel.grid.minor = element_blank(),
      plot.background = element_rect(fill = "floralwhite", color = "floralwhite")
    )
}

nba <- adv %>%
  ggplot(aes(x=as.numeric(ORtg), y = as.numeric(DRtg), label = Team))+
  geom_smooth(method="lm", color = "gray25", fill = "gray20")+
  geom_point(aes(fill = "red", color = after_scale(clr_darken(fill, 0.3))),
             shape = 21, 
             alpha =.75,
             size = 3)+
  geom_text_repel(size = 2, color = "black", min.segment.length = unit(0.1, "lines"))+
  theme_jelly()+
  theme(
    legend.position = "none",
    axis.line = element_line(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    plot.title = element_text(color = "black", hjust = .5, face = "bold", size = 15),
    plot.subtitle = element_text(color = "gray10", hjust = .5, face = "bold", size = 8))+
  labs(title = "Offensive Rating of NBA Teams",
       subtitle = "2022-23 Regular Season || Data:BBallRef\n",
       x = "Offensive Rating",
       y = "Defensive Rating",
       scale_y_reverse()
  )

ggsave("mid_season.png", nba, height = 6, width = 6, dpi = 300)





```


